### 2020-04-27 writeup/setup.tex
reorg

\begin{algorithm}[!t]
	\caption{Comparing the generalization error of MTL, TL and STL estimators}
	\begin{algorithmic}[1]
		\Input $(X_1, Y_2)$, $(X_2, Y_2)$.
		\Param Shared body $B$, task-specific prediction heads $W_1, W_2$.
		\State Training the shared body $B$.
		\State Optimizing the task heads on the validation set

		\begin{itemize}
			\item Jointly optimizing both tasks: $\hat{\beta}_t^{\MTL}$
			\item Optimizing the target task: $\hat{\beta}_t^{\TL}$
			\item Single-task training baseline: $\hat{\beta}_t^{\STL}$
		\end{itemize}
		\State Problem statement: Provide conditions to compare the test error of three estimators on the target task, $\te(\hat{\beta}_t^{\MTL})$, $\te(\hat{\beta}_t^{\STL})$ and $\te(\hat{\beta}_t^{\TL})$.
	\end{algorithmic}
\end{algorithm}

We state our main result for two tasks with both covariate and model shift in the following theorem.

\begin{theorem}\label{thm_model_shift}
	Let $n_1, n_2$ be the number of data points for the source, target task, respectively.
	Let $\hat{w}$ denote the optimal solution for the ratio $w_1/w_2$ in equation \eqref{eq_val_mtl}.
	Let ${M} = \hat{w} \Sigma_1^{1/2}\Sigma_2^{-1/2}$ denote the weighted covariate shift matrix.
	Denote by ${\lambda}_1, {\lambda}_2, \dots, {\lambda}_p$ the singular values of ${M}^{\top}{M}$.
	The information transfer is solely determined by two deterministic quantities $\Delta_{\beta}$ and $\Delta_{\vari}$, which show the change of model shift bias and variace, respectively.
	With high probability we have
	\begin{align}
	 	\te(\hat{\beta}_{t}^{\MTL}) \le \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \ge \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta \label{upper}\\
		\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL}) \text{ when: } &\Delta_{\vari} - \Delta_{\beta} \le -2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta, \label{lower}
	\end{align}
	where $\delta = \norm{Z} \cdot \norm{\Sigma_1^{1/2}(\beta_s - \hat{w}\beta_t)}^2$ with $Z = \frac{n_1^2}{(n_1 + n_2)^2}\cdot{M} \frac{(1 + a_3)\id + a_4 {M}^{\top}{M}}{(a_2 + a_1 {M}^{\top}{M})^2} {M}^{\top}$, and
	\begin{align*} %\bigtr{{\Sigma_2^{-1}}}
		\Delta_{\vari} &\define {\sigma^2}\bigbrace{\frac{p}{n_2 - p} -  \frac{1}{n_1 + n_2} \bigtr{(a_1 M^{\top}M + a_2\id)^{-1}} } \\
		\Delta_{\beta} &\define (\beta_s - \hat{w}\beta_t)^{\top} \Sigma_1^{1/2} Z \Sigma_1^{1/2} (\beta_s - \hat{w}\beta_t),
	\end{align*}
%	{\color{blue}To write the bounds in the form \eqref{upper} and \eqref{lower}, we have to define $\wh w$ as the minimizer of
%	$$\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w).$$
%	Otherwise, the two bounds has to be written into the form
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\ge \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}} + \Delta_\beta(w)+ \left(\bigbrace{1 + \sqrt{\frac{p} {n_1}}}^4 - 1 \right) \delta(w)\right\},
%	\end{align*}
%	and
%	\begin{align*}
%	{\sigma^2}\frac{p}{n_2 - p}\le \min_w \left\{\frac{\sigma^2}{n_1 + n_2} \bigtr{\frac1{a_1(w) M(w)^{\top}M(w) + a_2(w)\id}}+ \Delta_\beta(w) - 2\bigbrace{2\sqrt{\frac {p}{n_1}} + \frac{p}{n_1}} \delta(w)\right\}.
%	\end{align*}
%	}
%
%
	and $a_1, a_2, a_3, a_4$ are the solutions of the following linear equations
	\begin{gather}
		 a_1 + a_2 = 1- \frac{p}{n_1 + n_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(n_1 + n_2)(a_1 + a_2/ \lambda_i^2)} = \frac{n_1}{n_1 + n_2}, \label{eq_a2} \\
		\left(\frac{n_2}{a_2^2}- \sum_{i=1}^p \frac{1}{ (a_2 + \lambda_i^2a_1)^2  }\right) a_3 -  \left(\sum_{i=1}^p \frac{  \lambda_i^2 }{ (  a_2 + \lambda_i^2a_1)^2  }\right)a_4
		= \sum_{i=1}^p \frac{1 }{ (  a_2 + \lambda_i^2a_1)^2  }, \label{eq_a3} \\
		\left(\frac{n_1}{a_1^2} -  \sum_{i=1}^p \frac{\lambda_i^4   }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_4 -\left(\sum_{i=1}^p \frac{\lambda_i^2  }{  (a_2 + \lambda_i^2a_1)^2  }\right)a_3
		= \sum_{i=1}^p \frac{\lambda_i^2 }{  (a_2 + \lambda_i^2a_1)^2  }. \label{eq_a4}
	\end{gather}
\end{theorem}

%	We have the following conditions that guarantee the type of transfer we can get under model shift.
%	\begin{itemize}

%		\item {\bf Negative transfer:} we have $\te(\hat{\beta}_{s,t}) \ge \te(\hat{\beta}_t)$ when
%			\begin{align}
%				\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%			\end{align}
%	\end{itemize}
%	\begin{align}
%		{\Delta_{\vari}} \ge \bigbrace{1 + \sqrt{\frac{p}{n_1}}}^2 {\Delta_{\beta}},
%\label{eq_model_shift_pos}
%	\end{align}
%	where
%{\cob
%We have that
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\le ~ \Delta_\beta^{1/2}+ \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),\\
%		\end{align*}
%		and
%	\begin{align*}
%		&~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}} \\
%		&\ge ~ \Delta_\beta^{1/2}- \left\|M\frac{(1 + a_3)\id + a_4 M^{\top}M}{(a_1 + a_2 M^{\top}M)} M^{\top}\right\|_{op}^{1/2} \|\Sigma_1^{1/2} (\beta_s - \beta_t)\|_2 \left( 2\sqrt{\frac{p} {n_1}} + \frac{p}{n_1}\right),
%	\end{align*}
%	In the case where the entries of $\beta_s-\beta_t$ are i.i.d. random variables and $\Sigma_1=\id$, we have
%\begin{align*}
%		& \Delta_\beta\left( 1-\sqrt{\frac{p}{n_1}}\right)^4 \le ~ {\bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \beta_t)}}^2 \le ~
%\Delta_\beta\left( 1+\sqrt{\frac{p}{n_1}}\right)^4.
%		\end{align*}
%	}

Theorem \ref{thm_model_shift} shows upper and lower bounds that guarantee positive transfer, which is determined by the change of variance $\Delta_{\vari}$ and a certain model shift bias parameter $\Delta_{\beta}$ determined by the covariate shift matrix and the model shift.
The bounds get tighter and tighter as $n_1 / p$ increases.
%\paragraph{Negative transfer: the Limit caused by model shifts.}
%Next we describe lower bounds that guarantee negative transfer to complement Theorem \ref{thm_model_shift}.
%\begin{theorem}[Negative transfer under model shift]\label{thm_model_shift_neg}
%	In the setting of Theorem \ref{thm_model_shift}, we have $\te(\hat{\beta}_{s,t}) \ge
%\te(\hat{\beta}_t)$ when
%	\begin{align*}
%		\Delta_{\vari} \le \bigbrace{1 - 4\sqrt{\frac{p}{n_1}} - \frac{2p}{n_1}} {\Delta_{\beta}}
%	\end{align*}
%	In the special case that $\beta_s - \beta_t$ is i.i.d. with mean $0$ and variance $d^2$ and $\Sigma_1 = \id$, we can get a tighter lower bound that guarantees negative transfer when
%\begin{align}
%	\Delta_{\vari} \le \bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\beta}.\label{eq_model_shift_neg}
%\end{align}
%
%\end{theorem}

%From Lemma \ref{lem_cov_shift}, we know that
%\[ \bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} = \frac{1}{n_1 + n_2}\cdot \bigtr{ \bigbrace{a_1\Sigma_2^{-1/2}\Sigma_1\Sigma_2^{-1/2} + a_2\id}^{-1}}, \]
%where $a_1, a_2$ are specified in Theorem \ref{thm_cov_shift}.
%Hence the variance part is reduced by the following amount
%\begin{align}
%	\Delta_{\vari} \define \sigma^2 \cdot \bigbrace{\frac{p}{n_2 - p} - \frac{1}{n_1 + n_2} \bigtr{\bigbrace{a_1 M^{\top}M + a_2\id}^{-1}}}
%\end{align}
%It remains to consider the increment from the first term in $\te(\hat{\beta}_{s,t})$, which is bounded using the following lemma.
%We are now interested in the following quantity

\section{Preliminaries and Related Work}

>>>>

\section{Preliminaries}
